Asymmetric relationships and their effects on coexistence

### 2023-09-29 paper/Paper.Rnw
added zenodo record number
minor changes to the location of the data accessibility statement, to satisfy publisher formatting requests

\noindent \textbf{Running head:} Asymmetric relationships and coexistence \\
\noindent \textbf{Key words:} asymmetric tail association, biodiversity, coexistence, competition, copula, modern coexistence theory, niche differentiation, storage effects \\
\noindent \textbf{Type of article:} Letter\\
\noindent \textbf{Words in Abstract:} 150; \textbf{Words in main text:} 4998; \textbf{Words in text boxes:} 0\\
\noindent \textbf{Number of references:} 40; \textbf{Number of figures:} 5; \textbf{Number of tables:} 1; \textbf{Number of text boxes:} 0\\
\noindent \textbf{Corresponding author:}
Daniel C. Reuman,
Department of Ecology and Evolutionary Biology,
University of Kansas,
2101 Constant Ave,
Lawrence, KS 66047;
Phone: 626-560-7084 \\
\noindent \textbf{Author emails:} pimsupaa@uoregon.edu, reuman@ku.edu\\
\noindent \textbf{Statement of Authorship:} The authors jointly carried out all parts of the study.\\
\noindent \textbf{Data accessibility statement:} All codes associated with this study have been released in a 
public repository.

@@

\section{Data availability statement}

All code and data for the project are available at \url{https://zenodo.org/record/XXX}
%DAN: update when you know
and \url{https://github.com/jasminalbert/AsymmetricRelationshipsAndCoexistence}.

>>>>

\noindent \textbf{Running head:} Asymmetric relationships and coexistence \\
\noindent \textbf{Key words:} asymmetric tail association, biodiversity, coexistence, competition, copula, modern coexistence theory, niche differentiation, storage effects \\
\noindent \textbf{Type of article:} Letter\\
\noindent \textbf{Words in Abstract:} 150; \textbf{Words in main text:} 4998; \textbf{Words in text boxes:} 0\\
\noindent \textbf{Number of references:} 40; \textbf{Number of figures:} 5; \textbf{Number of tables:} 1; \textbf{Number of text boxes:} 0\\
\noindent \textbf{Corresponding author:}
Daniel C. Reuman,
Department of Ecology and Evolutionary Biology,
University of Kansas,
2101 Constant Ave,
Lawrence, KS 66047;
Phone: 626-560-7084 \\
\noindent \textbf{Author emails:} pimsupaa@uoregon.edu, reuman@ku.edu\\
\noindent \textbf{Statement of Authorship:} The authors jointly carried out all parts of the study.\\
\noindent \textbf{Data accessibility statement:} All code and data for the project are available 
at \url{https://zenodo.org/record/8386993} and 
\url{https://github.com/jasminalbert/AsymmetricRelationshipsAndCoexistence}.

@@
